Benchmarking FDR Methods - Summarizing Simulation Results

### 2017-12-07 datasets/simulations/analysis-03-plot-tsim-summaries.Rmd
Plot results for 'BL style' sims w/ 20% alt tests

@@

@@

>>>>

<!-- ######################################################################## -->
### Manual Covariate (Step - Less Informative)

```{r}
f <- "data-tsim/M100/esize_fixed-bl-step-less/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Effect Size, Manual Covariate (step - less informative) (100 replications)",
         tsb, cutoffs)
```

<!-- ######################################################################## -->
### Manual Covariate (Step - More Informative)

```{r}
f <- "data-tsim/M100/esize_fixed-bl-step-more/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Effect Size, Manual Covariate (step - more informative) (100 replications)",
         tsb, cutoffs)
```

<!-- ######################################################################## -->
### Manual Covariate (Cubic)

```{r}
f <- "data-tsim/M100/esize_fixed-bl-cubic/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Effect Size, Manual Covariate (cubic) (100 replications)",
         tsb, cutoffs)
```

@@

<!-- ######################################################################## -->
### Manual Covariate (Step - Less Informative)

```{r}
f <- "data-tsim/M100/n-bl-step-less/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Sample Sizes, Manual Covariate (step - less informative) (100 replications)",
         tsb, cutoffs)
```

<!-- ######################################################################## -->
### Manual Covariate (Step - More Informative)

```{r}
f <- "data-tsim/M100/n-bl-step-more/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Sample Sizes, Manual Covariate (step - more informative) (100 replications)",
         tsb, cutoffs)
```

<!-- ######################################################################## -->
### Manual Covariate (Cubic)

```{r}
f <- "data-tsim/M100/n-bl-cubic/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Sample Sizes, Manual Covariate (cubic) (100 replications)",
         tsb, cutoffs)
```

@@

<!-- ######################################################################## -->
### Manual Covariate (Step - Less Informative)

```{r}
f <- "data-tsim/M100/esize_random-bl-step-less/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Randomly Sampled Effect, Manual Covariate (step - less informative) (100 replications)",
         tsb, cutoffs)
```

<!-- ######################################################################## -->
### Manual Covariate (Step - More Informative)

```{r}
f <- "data-tsim/M100/esize_random-bl-step-more/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Randomly Sampled Effect, Manual Covariate (step - more informative) (100 replications)",
         tsb, cutoffs)
```

<!-- ######################################################################## -->
### Manual Covariate (Cubic)

```{r}
f <- "data-tsim/M100/esize_random-bl-cubic/results-performanceMetrics-alpha05.rds"
tsb <- readRDS(f)

## summarize results in plot
gen_plot("Two-Sample T-Tests w/ Varying Randomly Sampled Effect, Manual Covariate (cubic) (100 replications)",
         tsb, cutoffs)
```
